Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-23 paper.tex
Center figures
Describe data processing in more detail

From each set of tows, a standard time interval was set, and each run was
analyzed to compute statistics over this interval, truncating the end slightly
to achieve and integer number of blade passages.

The experimental data and processing/plotting code are available from
\cite{Bachant2015-RVAT-Re-dep-data}.

@@

\begin{figure}[ht]
\includegraphics[width=0.95\textwidth]{figures/perf_curves}
\caption{Mean power (left) and drag (right) coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:perf-curves}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.95\textwidth]{figures/perf_re_dep}
\caption{Mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.} 
\label{fig:perf-Re-dep}
\end{figure}

>>>>

From each set of tows, a standard time interval was set, which allowed the
turbine performance and wake to reach a quasi-periodic state. Each run was
analyzed to compute statistics over this interval, truncating the end slightly
to achieve and integer number of blade passages. Turbine shaft angular velocity
and tow carriage speed were calculated using a second order central differencing
scheme on the respective position measurements. Power and drag coefficients are
calculated as instantaneous quantities using the carriage speed as the free
stream velocity.

Wake velocity data were filtered for spurious ``spikes'' by removing datapoints
8 standard deviations or 0.9 m/s from the mean. The experimental data and code
for processing and visualization are available from
\cite{Bachant2015-RVAT-Re-dep-data}.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/perf_curves}
\caption{Mean power (left) and drag (right) coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:perf-curves}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/perf_re_dep}
\caption{Mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.} 
\label{fig:perf-Re-dep}
\end{figure}
